\documentclass[]{article}

\usepackage[none]{hyphenat}

%\usepackage{ifpdf}
%\ifpdf
%\usepackage[pdftex]{hyperref}
%\else
%\usepackage[hypertex]{hyperref}
%\fi

%\raggedright
%\linespread{1.2}
%\textheight = 700pt
%\textwidth = 370pt
%\hoffset = -37pt
%\voffset = -50pt
\pagestyle{empty}
%\righthyphenmin=55


\begin{document}

\begin{flushright}
	Ivan Martynov\\
  Huhtiniemenkatu 19 C 20\\
	53810 Lappeenranta, FINLAND\\
	+358 44 936 6589\\
	ivan.a.martynov [at] gmail.com\\
	\today
\end{flushright}

%\begin{flushleft}
%    FI-00520 Helsinki\\
%    FINLAND
%\end{flushleft}

%\begin{center}
%Gameplay Programmer Application
%\end{center}

\noindent
Dear Hiring Manager,
\bigskip

%\noindent
Please accept my cover letter for a Date Scientist position at Eniram.  Creating
mathematical models for the analysis of ship operations sounds interesting and
intriguing. I have skills in Linux OS, Python, C/C++, Java, Matlab as well as
strong mathematical background from Petrozavodsk State University.

Therefore, I would be happy to participate in scientific work at Eniram and
help building mathematical models.

During my master studies at Lappeenranta University of Technology I have been
working with 3D point clouds, including the use of Delaunay triangulation
routine to compute certain features of those points (Betti numbers). My master
thesis can be found at http://www.doria.fi/handle/10024/42533.

Later on I have earned experience in image processing and camera/projector
calibration with the help of Matlab and C++ libraries. Recently I have created
a set of Matlab functions and routines for calculating shadow areas using
geographical elevation data.

I hope to have my sleeves rolled up and start hands-on work with your team.
\\\ \\

\noindent
I thank you in advance for your consideration.\\\ \\

\noindent Sincerely,\\
Ivan Martynov

\end{document}

