\documentclass[]{article}

\usepackage[none]{hyphenat}

\usepackage{xcolor}
\definecolor{my_gray}{gray}{0.2}

\usepackage{ifpdf}
\ifpdf
\usepackage[pdftex]{hyperref}
\else
\usepackage[hypertex]{hyperref}
\fi
\hypersetup{colorlinks=true, urlcolor=my_gray}

%\raggedright
%\linespread{1.2}
%\textheight = 700pt
%\textwidth = 370pt
%\hoffset = -37pt
%\voffset = -50pt
\pagestyle{empty}
%\righthyphenmin=55


\begin{document}

\begin{flushright}
	Ivan Martynov\\
  Huhtiniemenkatu 19 C 20\\
	53810 Lappeenranta, FINLAND\\
	+358 44 936 6589\\
	ivan.a.martynov [at] gmail.com\\
	\today
\end{flushright}

\begin{flushleft}
  Fortum\\
  Keilaniemi\\
  P.O. BOX 1\\
  00048 FORTUM\\
  FINLAND
\end{flushleft}

\begin{center}
  Quantitative Developer\,/\,Applied Mathematician Application
\end{center}

\noindent
Dear Hiring Manager,
\bigskip

\noindent
Please accept my application for the Quantitative Developer\,/\,Applied
Mathematician position. I would be happy to participate in the development and
maintenance of optimization solutions. The opportunity to become a better expert
and do something exceptional sounds very attractive.

\medskip
\noindent
During my master studies at Lappeenranta University of Technology I have been
working with 3D point clouds, including the use of Delaunay triangulation
routine to compute certain features of those points (Betti numbers). My master
thesis can be found at \href{http://www.doria.fi/handle/10024/42533}
{http://www.doria.fi/handle/10024/42533}.

\medskip
\noindent
Later on I have earned experience in image processing and camera/projector
calibration with the help of Matlab and C++ libraries. Recently I have created a
set of Matlab functions and routines for calculating shadow areas using
geographical elevation data.

\medskip
\noindent
Thus I can say that my experience with Matlab is rather broad. I enjoy coding
and am always trying to produce the most clean, optimized and reusable code.
Obviously, the learning process never ends and I am eager to develop my skills
specifically for the optimization solutions in the energy systems and continue
with such an experienced and respected company as Fortum.

\medskip
\noindent
I hope to have my sleeves rolled up and start hands-on work with the System
Optimization team.
\\\ \\

\noindent
I thank you in advance for your consideration.\\\ \\

\noindent Sincerely,\\
Ivan Martynov

\end{document}

