\documentclass[]{article}

\usepackage[none]{hyphenat}

%\usepackage{ifpdf}
%\ifpdf
%\usepackage[pdftex]{hyperref}
%\else
%\usepackage[hypertex]{hyperref}
%\fi

%\raggedright
%\linespread{1.2}
%\textheight = 700pt
%\textwidth = 370pt
%\hoffset = -37pt
%\voffset = -50pt
\pagestyle{empty}
%\righthyphenmin=55


\begin{document}

\begin{flushright}
	Ivan Martynov\\
  Huhtiniemenkatu 19 C 20\\
	53810 Lappeenranta, FINLAND\\
	+358 44 936 6589\\
	ivan.a.martynov [at] gmail.com\\
	\today
\end{flushright}

%\begin{flushleft}
%  Karmina Aquino\\
%  F-Secure\\
%  Tammasaarenkatu 7\\
%  Helsinki, FINLAND
%\end{flushleft}

\begin{center}
  Data Analyst Application
\end{center}

\noindent
Dear Hiring Manager,
\bigskip

\noindent
Please accept my cover letter for the Data Analyst position at Nordea.
The opportunity to fight crime, even financial, sounds thrilling and I would be
happy to employ my analytical and programming skills towards the noble goal.
\medskip

\noindent
My programming skills are coming from a variety of languages: C/C++, Pyhton,
Java, Matlab, Pascal, Prolog and some others with Matlab being used mostly. I
have started coding in 2002 and picking up new languages\,/\,technologies is no
problem for me.
\medskip

\noindent
I am currently pursuing my Ph.D. degree at Lappeenranta University of
Technology and have created a set of Matlab functions and routines to
calculate shadow areas using geographical elevation data.
\medskip

\noindent
During master studies I have been working with 3D point clouds, including the
use of Delaunay triangulation routine to compute certain features of those
points (Betti numbers).
\noindent
Studying in Lappeenranta has also introduced me to the multicultural environment
and I was welcome, giving a great experience. Thus, communicating with people is
usually not bringing any trouble.
\medskip

\noindent
Later on I have earned experience in image processing and camera/projector
calibration with the help of Matlab and C++ libraries.
\medskip

\noindent
I enjoy coding and always strive to produce the most clean, optimized and
reusable code. Obviously, the learning process never ends and I am eager to
develop my skills specifically for the data analysis, simulations and models
development aiming for most optimal and secure solutions.  Hopefully, my sleeves
will soon be rolled up and I shall start hands-on work with the team of Nordea
experts!
\medskip

\noindent
I thank you in advance for your consideration.\\\ \\

\noindent Sincerely,\\
Ivan Martynov

\end{document}
