\documentclass[]{article}

\usepackage[none]{hyphenat}

%\usepackage{ifpdf}
%\ifpdf
%\usepackage[pdftex]{hyperref}
%\else
%\usepackage[hypertex]{hyperref}
%\fi

%\raggedright
%\linespread{1.2}
%\textheight = 700pt
%\textwidth = 370pt
%\hoffset = -37pt
%\voffset = -50pt
\pagestyle{empty}
%\righthyphenmin=55


\begin{document}

\begin{flushright}
	Ivan Martynov\\
  Huhtiniemenkatu 19 C 20\\
	53810 Lappeenranta, FINLAND\\
	+358 44 936 6589\\
	ivan.a.martynov [at] gmail.com\\
	\today
\end{flushright}

%\begin{flushleft}
%  Karmina Aquino\\
%  F-Secure\\
%  Tammasaarenkatu 7\\
%  Helsinki, FINLAND
%\end{flushleft}

\begin{center}
  Software developer\,/\,Analyst trainee Application
\end{center}

\noindent
Dear Hiring Manager,
\bigskip

\noindent
Please accept my cover letter for the position of Software developer\,/\,Analyst
trainee at Posti Group. The opportunity to develop software with data analysis
tasks is a great chance to have my analytical and programming skills applied.
\medskip

\noindent
My programming skills are coming from a variety of languages: C/C++, Pyhton,
Java, Matlab, Pascal, Prolog and some others. I have started coding in 2002 and
picking up new languages\,/\,technologies is no problem for me.
\medskip

\noindent
Currently, I am pursuing my Ph.D. degree at Lappeenranta University of
Technology. I have devised a set of Matlab functions and routines to
calculate shadow areas using satellite geographical elevation data.
\medskip

\noindent
During master studies I have been working with 3D point clouds, including the
use of Delaunay triangulation routine to compute Betti numbers.  Later on I have
earned experience in image processing and camera/projector calibration with the
help of Matlab and C++ libraries.
\medskip

\noindent
I enjoy coding and always strive to produce the most clean, optimized and
reusable code. Obviously, the learning process never ends and I am eager to
develop my skills further specifically for the development of analysis and
planning software. Hopefully, my sleeves will soon be rolled up and I shall
start hands-on work with the team of Posti experts!
\medskip

\noindent
I thank you in advance for your consideration.\\\ \\

\noindent Sincerely,\\
Ivan Martynov

\end{document}
