\documentclass[]{article}

\usepackage[none]{hyphenat}

%\usepackage{ifpdf}
%\ifpdf
%\usepackage[pdftex]{hyperref}
%\else
%\usepackage[hypertex]{hyperref}
%\fi

%\raggedright
%\linespread{1.2}
%\textheight = 700pt
%\textwidth = 370pt
%\hoffset = -37pt
%\voffset = -50pt
\pagestyle{empty}
%\righthyphenmin=55


\begin{document}

\begin{flushright}
	Ivan Martynov\\
  Huhtiniemenkatu 19 C 20\\
	53810 Lappeenranta, FINLAND\\
	+358 44 936 6589\\
	ivan.a.martynov [at] gmail.com\\
	\today
\end{flushright}

%\begin{flushleft}
%    FI-00520 Helsinki\\
%    FINLAND
%\end{flushleft}

\begin{center}
  Junior Data Analyst Application
\end{center}

\noindent
Dear Hiring Manager,
\bigskip

\noindent
Please accept my cover letter for a Junior Data Analyst Application position at
Rovio. I would be happy to apply my analytical skills for the game development
and finding the best solutions for analytics.
\medskip

\noindent
During my master studies at Lappeenranta University of Technology I have been
working with 3D point clouds, including the use of Delaunay triangulation
routine to compute certain features of those points (Betti numbers). My master
thesis can be found at http://www.doria.fi/handle/10024/42533.
\medskip

\noindent
Later on I have earned experience in image processing and camera/projector
calibration with the help of Matlab and C++ libraries. Recently I have created
a set of Matlab routines for calculating shadow areas using
geographical elevation data.
\medskip

\noindent
Currently, most of my free time is devoted for learning computer graphics and
improving my C++ skills. Obviously, the learning process never ends and I am
eager to develop my skills specifically for the analysis of game data and
continue with such an experienced and game developer as Rovio.
\medskip

\noindent
Games have been a part of my life for a couple of decades and many of them
fascinated me to various levels. They have been gradually increasing my
curiosity about how games are made and thus ripening my decision to become a
game programmer. I have taken several university and Coursera.org courses
dedicated to games, went through various on-line material. Now, after studying
and practising the concepts of game design I have a better understanding how
the games are created.
\medskip

\noindent
I am strongly motivated to be an analyst in the gaming world and I am sure my
skills will be useful for programming tasks you games require to be done. I hope
to have my sleeves rolled up and start hands-on work with the Rovio team.
\\\ \\

\noindent
I thank you in advance for your consideration.\\\ \\

\noindent Sincerely,\\
Ivan Martynov

\end{document}
