\documentclass[]{article}

\usepackage[none]{hyphenat}

%\usepackage{ifpdf}
%\ifpdf
%\usepackage[pdftex]{hyperref}
%\else
%\usepackage[hypertex]{hyperref}
%\fi

%\raggedright
%\linespread{1.2}
%\textheight = 700pt
%\textwidth = 370pt
%\hoffset = -37pt
%\voffset = -50pt
\pagestyle{empty}
%\righthyphenmin=55


\begin{document}

\begin{flushright}
	Ivan Martynov\\
  Huhtiniemenkatu 19 C 20\\
	53810 Lappeenranta, FINLAND\\
	+358 44 936 6589\\
	ivan.a.martynov [at] gmail.com\\
	\today
\end{flushright}

%\begin{flushleft}
%    RedLynx Ltd.\\
%    Kumpulantie 3\\
%    FI-00520 Helsinki\\
%    FINLAND
%\end{flushleft}

%\begin{center}
%Graduate Program, Gameplay Programmer Application
%\end{center}

\noindent
Dear Hiring Manager,
\bigskip

\noindent
Please accept my cover letter for the Junior Programmer position at Umbra.
I would be happy to have a chance to work at Umbra with 3D geometry, learn how
the mathematical models are built at your company and put my best effort to
prove worth being part of the team.

During my master studies at Lappeenranta University of Technology I have been
working with 3D point clouds, including the use of Delaunay triangulation
routine to compute certain features of those points (Betti numbers). Later on I
have earned experience in image processing and camera/projector calibration
with the help of Matlab and C++ libraries. Recently I have created a set of
Matlab functions and routines to calculate shadow areas using geographical
elevation data.

Thus computing various world features of using 3D data has long been an
interest for me and I would love to continue in this direstion. Therefore, the
opened opportunity at Umbra is perfect and the perspective of jumping right
into the deeps of production code chain sounds thrilling and exciting for me.
%\medskip

%\noindent
%I have played many games for nearly twenty years and at some point started to
%think how they are made. I have taken several university and Coursera.org
%courses dedicated to games, went through various on-line material. Now, after
%studying and practicing the concepts of game design I have a better
%understanding how the games are created.
%\medskip

I enjoy coding and I am always trying to produce the most clean, optimized and
reusable code. The C++ language strikes with its versatility and beauty and it
amuses me more than other languages. Obviously, the learning process never ends
and I am eager to develop my skills specifically for 3D graphics and continue
with such an experienced and respected company as Umbra.

%\medskip
Games have been a part of my life for a couple of decades and many of them
fascinated me to various levels. One of the games which has left a memorable
mark is World of Tanks with its astonishing display of details and vividness.
This game is a product of Wargaming.net (one of the Umbra clients) so it is nice
to actually observe what kind of aims work at Umbra might have. Seeing results
is a great motivation and I hope to have my sleeves rolled up and start
hands-on work with your team.
\\\ \\

\noindent
I thank you in advance for your consideration.\\\ \\

\noindent Sincerely,\\
Ivan Martynov

\end{document}
