\documentclass{article}

\begin{document}

\begin{center}
\Large{\bf{Possible Q \& A During an Interview}}
\end{center}

\begin{enumerate}

  \item What are responsibilities and tasks for this job and would you be a
    dream candidate for this position?\\
    Work in a team to meet project milestones.
    Work with design teams to tune and enhance game dynamics.
    My task is to write a code (in C++) for game components (would it be an AI
    or UI or something else) to be incorporated into a large game project.\\
    gameplay programmer focuses more on a game's strategy, implementation of
    the game's mechanics and logic, and the ``feel'' of a game.\\
    may implement strategy tables, tweak input code, or adjust other factors
    that alter the game.\\
    Write a C++ code which is to be incorporated into a component of a bigger
    program. I am responsible to produce a solid, clean, maintanable, efficient
    code. Ensure that the code meets functional and performance requirements.\\
    My goal are definite, I have a strong will to be a game developer, I want
    to make games\\

    My task is to write a C++ code for game components with focus on the
    strategy, mechanics and logic of the games. I am responsible to ensure that
    the delivered code is clean, functional and meets the performance
    requirements.
    I am a dream candidate for this posistion because, besides having
    qualifications, I am well determined that I want to make games and
    confident that I can excel at this role.

  \item Describe your strategy for the first 90 days.\\
    Get to know the people and the environment in my department, familiarize
    myself with the software tools and start creating code. I would propose
    regular  meetings with supervisors (weekly or every second week) to track
    the progress and see if we are heading the right direction. Next, get to
    know the key persons in the other departments. That would help to ensure
    that our project milestones are met.

  \item What is your greatest failure and what did you learn from it?\\
    Failing at entering to the University, perfectly passing the math exam and
    performing not so well at the physics exam. I have learned to be prepared
    well beforehand. After the failure I was working (as a cook) from 7am till
    3--4~pm and staying after the work in the kitchen, doing homework and then
    going to the University around 6pm to the pre-study courses (math,
    physics, literature). Later I successfully passed the enrollment exams and
    proved to be one of the best students in my specialization (math).

  \item If you were a superhero, who would you be?
  Let's see\ldots I like math and who is good at math?\\
  I would like to be someone like Tony Stark, whose math is always correct, he
  is genius, great at physics and mechanics, not counting mathematics.
  It doesn't hurt being a genius.
  Kind of Iron Man

\end{enumerate}

\end{document}
